---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

## Shiny server for the metaPR2 database

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/191439796.svg)](https://zenodo.org/badge/latestdoi/191439796)
<!-- badges: end -->


An [interactive database](https://app.metapr2.org/) of eukaryotic metabarcodes compiled from the literature. 

### Presentation

MetaPR2 is a database of published 18S rRNA metabarcodes. This R package launches a shiny application that allows to interact with the database by mapping, searching and downloading the barcodes.

### How run the metaPR2 shiny server

#### Step 1 - Install the R package from GitHub

If you are running Windows install Rtools

[https://cran.r-project.org/bin/windows/Rtools/](https://cran.r-project.org/bin/windows/Rtools/)

Run the following line from R studio

```{r}
# Allow installation form github
install.packages("devtools")

devtools::install_github("vaulot/metapr2-shiny")
```


#### Step 2 - Launch the metaPR2 shiny server


```{r example}
library(metapr2)
metapr2App()

```

### Panels

* **About**: Basic information on the metapr2 database
* **Datasets**: List of datasets used.
* **Map**: Maps of relative abundance. Taxonomic level can be chosen as well as sample types (RNA/DNA, substrate, depth layer...).
* **Treemap**: Create treemap graphs for samples and taxon selected
* **Query**: Enter a sequence and search for metabarcode that are similar to your sequence using BLAST like search.

### Data processing


* Total read number per sample has been normalized to 100 with 3 decimals so that the value displayed in the different panels correspond to % of total eukaryotic reads.

### Errors

Please report errors in the [Issues page of the metaPR2 primer database](https://xxx).


### Citation

Vaulot, D. et al. (2021). [metaPR2 : An interactive 18S rRNA metabarcode database](). Unpublished

### Resources
* Website: https://app.metapr2.org/
* Docker: https://hub.docker.com/repository/docker/vaulot/metapr2
* Source code: https://github.com/pr2database/metapr2

### Maintainer
* Daniel Vaulot: vaulot@gmail.com

### Contributors

* 

### Versions

1.0.0 - 2021-xx-xx
* Initial version