---
output: 
  github_document: default
  pdf_document: default
  html_document: default
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# metaPR2

**version 1.0.0** : 41 datasets

## A database of 18S rRNA metabarcodes

```{r, eval=FALSE, echo=FALSE}
<!-- badges: start -->
[![DOI](https://zenodo.org/badge/191439796.svg)](https://zenodo.org/badge/latestdoi/191439796)
<!-- badges: end -->
```

### Presentation

MetaPR2 is a database of published 18S rRNA metabarcodes that have been reprocessed and assigned using PR2. 

#### Data processing

* Raw fastq files were downloaded from NCBI or from author web site if not deposited to NCBI

* All datasets were processed with cutapdapt to remove primers and the dada2 R package to compute ASVs.

* Assignment was done with dada2 assignTaxa using the 18S PR2 4.14.0 as reference

* ASVs with less 100 reads total and with bootstrap value at the supergroup level < 90 were not considered.

* Total read number per sample has been normalized to 100 with 3 decimals so that the value displayed in the different panels correspond to % of total eukaryotic reads.

### Acessing the database

Access to the database to map, search and download the barcodes can be done in three different ways:

* Using a [web interface](https://metapr2-dcx2qwgoua-as.a.run.app/).

* Download the R package and launch the shiny application.

* Download and run a Docker container 

#### Web interface

* https://metapr2-dcx2qwgoua-as.a.run.app/

#### metaPR2 shiny R package
*(NOT YET AVAILABLE)*

Install the package from GitHub and launch function metapr2App()

```{r, eval=FALSE, echo=TRUE}

install.packages(devtools)

devtools::install_github("pr2database/metapr2-shiny")

metapr2::metapr2App()
```


#### The metaPR2 Docker container
*(NOT YET AVAILABLE)*

Will be available from Docker repository


### Errors

Please report errors in the [Issues page of the metaPR2 primer database](https://github.com/pr2database/metapr2-shiny/issues).


### Citation

Vaulot, D. et al. (2021). metaPR2 : An interactive 18S rRNA metabarcode database. Unpublished

```{r eval=FALSE, echo=FALSE}
TO ADD LATER

### Resources
* Website: https://shiny.metapr2.org/
* Docker: https://hub.docker.com/repository/docker/vaulot/metapr2
* Source code: https://github.com/pr2database/metapr2
```



### Maintainer
* Daniel Vaulot: vaulot@gmail.com

### Contributors

* Daniel Vaulot, CNRS Roscoff, NTU-ASE Geek lab
* Adriana Lopes dos Santos, NTU-ASE Geek lab 
* Clarence Sim, NTU-ASE Geek lab 
* Denise Ong, NTU-ASE Geek lab 
* Bryan Teo, NTU-ASE Geek lab
* Mahwash Jamy, Uppsala University Sweden
* Charlie Biwer, Uppsala University Sweden



