---
title: "Get started"
author: "Daniel Vaulot"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{get started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "#>" 
  # fig.path = "img/"   # Directories where image are saved
)
```


The metaPR2 shiny application allowing access to the metaPR2 database is provided as a R package called **metaPR2**.  This page provides instruction to install and use the package.  

# Installation

Install from the GitHub web site using the devtools package

```{r, eval=FALSE, echo=TRUE}

install.packages(devtools)

devtools::install_github("pr2database/metapr2-shiny")

```

# Run the Shiny application

```{r eval=FALSE }

metapr2::metapr2App()

```


#### Stop the Shiny application

* Close the browser window

OR

* Hit the stop button at the top right of the bottom left window


#### In case Shiny application crashes

* Hit the stop button at the top right of the bottom left window
* Relaunch `metapr2App()`